---
title: "SEB skills Insegnanti"
author: "Gerardo & Tommaso"
output:
  html_document:
    theme: cosmo
    toc: true
    toc_depth: 3
    toc_float: true
  pdf_document:
    toc: true
    toc_depth: '3'
    latex_engine: xelatex
---
# Before starting 

```{r Setup, message=FALSE, warning=FALSE, error=FALSE, include = FALSE}

R.Version()

rm(list = ls()) 
options(scipen = 999)

```

```{r Packages, message=FALSE, warning=FALSE, error=FALSE, include=FALSE}
library(psych)
library(dplyr)
library(tidyr)
library(corrplot)
library(ggplot2)
library(lavaan)
library(lme4)
library(readxl)
library(forcats)
library(janitor)
library(careless)
library(tibble)
library(ordinal)
library(stringr)
library(fmsb)
library(performance)
```

```{r Prepare the dataset, message=FALSE, warning=FALSE, error=FALSE, include = FALSE}
# Upload dataset 
d <- read_excel("InsegnantiSEB_data.xlsx", na = "NA")

# Code for participants
d <- d %>%
  mutate(Code = paste0("Code", row_number()))

# Convert questionnaire items to numeric
d <- d %>%
  dplyr::mutate(across(BESSI_1:Frequency_5, ~ as.numeric(.)))

d$Age <- as.numeric(d$Age)
d$Class_Time <- as.numeric(d$Class_Time)
d$Experience <- as.numeric(d$Experience)
d$Role <- as.factor(d$Role)

# Dummy variable for Grade
# Assuming your data frame is named `dcII` and has a column `School_Grade`
d <- d %>%
  mutate(
    Grade_Kindergarten = ifelse(School_Grade == 1, 1, 0),
    Grade_Primary      = ifelse(School_Grade == 2, 1, 0),
    Grade_Middle       = ifelse(School_Grade == 3, 1, 0),
    Grade_High         = ifelse(School_Grade == 4, 1, 0)
  )


```

```{r Data cleaning $ Datasets creation, message=FALSE, warning=FALSE, error=FALSE, include = FALSE}
# Dataset for screen classification 
# Exlude participants with more than 12 NA in BESSI items
dc <- d %>%
  dplyr::mutate(bessi_na_count = rowSums(is.na(select(., BESSI_1:BESSI_32)))) %>%
  filter(bessi_na_count <= 12) %>%
  select(-bessi_na_count)

# Careless responders
# Function to compute longstring ignoring NAs
compute_longstring <- function(vec) {
  vec <- vec[!is.na(vec)]  # Remove NAs
  if (length(vec) == 0) return(0)
  
  rle_res <- rle(vec)  # Run-length encoding
  return(max(rle_res$lengths))  # Return longest streak of identical values
}

# Apply to BESSI_1 to BESSI_32
dc$long_BESSI <- apply(dc[, paste0("BESSI_", 1:32)], 1, compute_longstring)
# Flag: longstring > 15
dc$long_BESSI_flag <- ifelse(dc$long_BESSI > 15, 1, 0)

# Use careless::longstring for Efficacy items (no missing)
# We considered also Efficacy items to have a double check 
dc$long_Efficacy <- longstring(dc[, paste0("Efficacy_", 1:10)])
dc$long_Efficacy_flag <- ifelse(dc$long_Efficacy > 7, 1, 0)

# Combine flags
dc$careless_flag <- dc$long_BESSI_flag + dc$long_Efficacy_flag
# Report flagged participants
table(dc$careless_flag)
# Optional: Keep only participants with 0 flags
dc <- dc %>% filter(careless_flag < 1)

```

```{r Create dataset for mixed model, message=FALSE, warning=FALSE, error=FALSE, include = FALSE}
# No missing data in all blocks
dcII <- dc %>%
  filter(
    if_all(c(Age:School_Grade, Efficacy_1:Role, Class_Time), ~ !is.na(.))
  )

# Check abnormal values in Class_Time
dcII <- dcII %>%
  filter(Class_Time <= 40)

```

```{r Scoring of questionnaires, message=FALSE, warning=FALSE, error=FALSE, include = FALSE}
# Efficacy scoring (subscales and total)
dcII <- dcII %>%
  mutate(
    Efficacy_Management = rowMeans(select(., Efficacy_1:Efficacy_4), na.rm = FALSE),
    Efficacy_Engagement = rowMeans(select(., Efficacy_5:Efficacy_6), na.rm = FALSE),
    Efficacy_Instruction = rowMeans(select(., Efficacy_7:Efficacy_10), na.rm = FALSE)
  )

dcII <- dcII %>%
  mutate(
    Efficacy_Total = rowMeans(select(., Efficacy_Management, Efficacy_Engagement, Efficacy_Instruction), na.rm = FALSE)
  )

# Commitment & Culture
dcII <- dcII %>%
  mutate(
    Culture = rowMeans(select(., `Culture&Committment_1`, `Culture&Committment_2`), na.rm = FALSE),
    Commitment = rowMeans(select(., `Culture&Committment_3`, `Culture&Committment_4`), na.rm = FALSE)
  )

# Frequency
dcII <- dcII %>%
  mutate(
    Frequency = rowMeans(select(., Frequency_1:Frequency_5), na.rm = FALSE)
  )

```

# Sample - Descriptive tables
## Total sample for BESSI classification
```{r Sample descriptive statistics, message=FALSE, warning=FALSE, error=FALSE, include = TRUE}
# Function to create a named vector of summaries
create_summary_vector <- function(data) {
  c(
    "Age (Mean)" = round(mean(data$Age, na.rm = TRUE), 2),
    "Age (SD)" = round(sd(data$Age, na.rm = TRUE), 2),
    
    "Experience (Mean)" = if ("Experience" %in% names(data)) round(mean(data$Experience, na.rm = TRUE), 2) else NA,
    "Experience (SD)" = if ("Experience" %in% names(data)) round(sd(data$Experience, na.rm = TRUE), 2) else NA,
    
    "Class Time (Mean)" = if ("Class_Time" %in% names(data)) round(mean(data$Class_Time, na.rm = TRUE), 2) else NA,
    "Class Time (SD)" = if ("Class_Time" %in% names(data)) round(sd(data$Class_Time, na.rm = TRUE), 2) else NA,
    
    "Gender: Male (1)" = sum(data$Gender == 1, na.rm = TRUE),
    "Gender: Female (2)" = sum(data$Gender == 2, na.rm = TRUE),
    "Gender: Non-binary (3)" = sum(data$Gender == 3, na.rm = TRUE),
    "Gender: Not disclosed (4)" = sum(data$Gender == 4, na.rm = TRUE),
    
    "Grade: Kindergarten (1)" = sum(data$School_Grade == 1, na.rm = TRUE),
    "Grade: Primary (2)" = sum(data$School_Grade == 2, na.rm = TRUE),
    "Grade: Middle (3)" = sum(data$School_Grade == 3, na.rm = TRUE),
    "Grade: High (4)" = sum(data$School_Grade == 4, na.rm = TRUE),
    
    "Education: High school (1)" = if ("Education" %in% names(data)) sum(data$Education == 1, na.rm = TRUE) else NA,
    "Education: Bachelor (2)" = if ("Education" %in% names(data)) sum(data$Education == 2, na.rm = TRUE) else NA,
    "Education: Master (3)" = if ("Education" %in% names(data)) sum(data$Education == 3, na.rm = TRUE) else NA,
    "Education: PhD/2nd Level (4)" = if ("Education" %in% names(data)) sum(data$Education == 4, na.rm = TRUE) else NA,
    
    "Role: Support (1)" = if ("Role" %in% names(data)) sum(data$Role == 1, na.rm = TRUE) else NA,
    "Role: Curricular (2)" = if ("Role" %in% names(data)) sum(data$Role == 2, na.rm = TRUE) else NA
  )
}

# Create vertical data frame
desc_dc <- create_summary_vector(dc)
desc_dcII <- create_summary_vector(dcII)

summary_table_vertical <- tibble(
  Variable = names(desc_dc),
  `dc (BESSI Sample)` = desc_dc,
  `dcII (Complete Sample)` = desc_dcII
)

knitr::kable(summary_table_vertical, digits = 2, caption = "Descriptive statistics of the sample")
```

## Descriptive for all variable
```{r Variables descriptive statistics, message=FALSE, warning=FALSE, error=FALSE, include = TRUE}
# Vector of variable names
agg_vars <- c("Efficacy_Management", "Efficacy_Engagement", "Efficacy_Instruction",
              "Efficacy_Total", "Culture", "Commitment", "Frequency")

# Descriptive stats table
desc_table <- dcII %>%
  select(all_of(agg_vars)) %>%
  summarise(across(everything(), list(
    N = ~sum(!is.na(.)),
    Mean = ~mean(., na.rm = TRUE),
    SD = ~sd(., na.rm = TRUE),
    Skewness = ~psych::skew(., na.rm = TRUE),
    Kurtosis = ~psych::kurtosi(., na.rm = TRUE),
    Min = ~min(., na.rm = TRUE),
    Max = ~max(., na.rm = TRUE)
  ), .names = "{.col}_{.fn}")) %>%
  pivot_longer(everything(),
               names_to = c("Variable", ".value"),
               names_pattern = "(.*)_(.*)") %>%
  relocate(Variable)

# Print in markdown-friendly format
knitr::kable(desc_table, digits = 2, caption = "Descriptive statistics for all variables")

```

# SEB skills classification

At the facet level, we classify the 32 skills based on teachers' confidence ratings, providing a classification of skills that teachers feel more/less confident about teaching.

```{r SEB skills descriptives, message=FALSE, warning=FALSE, error=FALSE, include = TRUE}
bessi_label_vec <- c(
  "Gestione dei compiti",
  "Gestione del tempo",
  "Attenzione ai dettagli",
  "Organizzazione degli spazi e dei materiali",
  "Gestione degli impegni",
  "Costanza",
  "Definizione degli obiettivi",
  "Aderenza alle regole",
  "Prendere decisioni",
  "Leadership",
  "Persuasione",
  "Fare conversazione",
  "Comunicazione",
  "Regolazione delle energie",
  "Collaborazione",
  "Sapersi fidare e saper perdonare",
  "Immedesimazione",
  "Accoglienza emotiva",
  "Affabilità e cordialità",
  "Gestione dello stress",
  "Ottimismo",
  "Gestione della rabbia",
  "Autostima",
  "Resistere alle tentazioni",
  "Pensiero astratto",
  "Creatività",
  "Espressione artistica",
  "Interculturalità",
  "Elaborazione delle informazioni",
  "Adattabilità",
  "Autonomia",
  "Introspezione"
)

# Create the lookup table
item_labels <- tibble(
  item = paste0("BESSI_", 1:32),
  skill = bessi_label_vec
)

item_stats <- dc %>%
  select(BESSI_1:BESSI_32) %>%
  summarise(across(everything(),
                   list(
                     n           = ~sum(!is.na(.)),
                     missing_pct = ~round(mean(is.na(.)) * 100, 2),
                     mean        = ~mean(., na.rm = TRUE),
                     sd          = ~sd(., na.rm = TRUE),
                     min         = ~min(., na.rm = TRUE),
                     max         = ~max(., na.rm = TRUE)
                   ),
                   .names = "{.col}_{.fn}")) %>%
  pivot_longer(everything(),
               names_to = c("item", ".value"),
               names_pattern = "(BESSI_\\d+)_(.*)") %>%
  # Compute SE and 95% CI
  mutate(
    se       = sd / sqrt(n),
    ci_lower = mean - 1.96 * se,
    ci_upper = mean + 1.96 * se
  ) %>%
  # Join with skill labels
  left_join(item_labels, by = "item") %>%
  # Rank items by mean confidence
  arrange(desc(mean)) %>%
  mutate(rank = row_number())

knitr::kable(item_stats, digits = 2, caption = "SEB skills ranking")

```

```{r Plot the ranking, message=FALSE, warning=FALSE, error=FALSE, include = TRUE}
item_stats <- dcII %>%
  summarise(across(
    starts_with("BESSI_"),
    list(
      N    = ~sum(!is.na(.x)),
      mean = ~mean(.x, na.rm = TRUE),
      sd   = ~sd(.x,   na.rm = TRUE)
    ),
    .names = "{.col}_{.fn}"
  )) %>%
  # Pivot longer so we have one row per BESSI item
  pivot_longer(
    everything(),
    names_to = c("item", ".value"),
    names_pattern = "(BESSI_\\d+)_(.*)"
  ) %>%
  # Compute standard error
  mutate(se = sd / sqrt(N))


# ─── STEP A: Create lookup vectors “by position” ────────────────────────────────
bessi_label_vec <- c(
  "Gestione dei compiti",
  "Gestione del tempo",
  "Attenzione ai dettagli",
  "Organizzazione degli spazi e dei materiali",
  "Gestione degli impegni",
  "Costanza",
  "Definizione degli obiettivi",
  "Aderenza alle regole",
  "Prendere decisioni",
  "Leadership",
  "Persuasione",
  "Fare conversazione",
  "Comunicazione",
  "Regolazione delle energie",
  "Collaborazione",
  "Sapersi fidare e saper perdonare",
  "Immedesimazione",
  "Accoglienza emotiva",
  "Affabilità e cordialità",
  "Gestione dello stress",
  "Ottimismo",
  "Gestione della rabbia",
  "Autostima",
  "Resistere alle tentazioni",
  "Pensiero astratto",
  "Creatività",
  "Espressione artistica",
  "Interculturalità",
  "Elaborazione delle informazioni",
  "Adattabilità",
  "Autonomia",
  "Introspezione"
)

domain_vec <- c(
  rep("Self-management",         9),  # BESSI_1–_9
  rep("Social Engagement",       5),  # BESSI_10–_14
  rep("Cooperation",             5),  # BESSI_15–_19
  rep("Emotional resilience",    5),  # BESSI_20–_24
  rep("Innovation",              5),  # BESSI_25–_29
  rep("Compound",                3)   # BESSI_30–_32
)


# ─── STEP B: Attach label & domain via index ───────────────────────────────────
item_stats <- item_stats %>%
  mutate(
    item    = as.character(item),
    idx     = as.integer(str_remove(item, "^BESSI_")),
    label   = bessi_label_vec[idx],
    Domain  = domain_vec[idx],
    Domain  = factor(Domain, levels = c(
                "Self-management",
                "Social Engagement",
                "Cooperation",
                "Emotional resilience",
                "Innovation",
                "Compound"
              )),
    label   = fct_reorder(label, mean)
  ) %>%
  select(-idx)


# ─── STEP C: Define domain colors ───────────────────────────────────────────────
domain_colors <- c( # Scusa, sono brutti ma si capisce meglio ;)
  "Self-management"      = "red", # "#1b9e77",
  "Social Engagement"    = "blue",  # "#d95f02",
  "Cooperation"          = "green", # "#7570b3",
  "Emotional resilience" = "black", # "#e7298a",
  "Innovation"           = "pink", # "#66a61e",
  "Compound"             = "#666666"
)


# ─── STEP D: Plot “mean ± 95% CI” for each BESSI item, colored by Domain ──────
ggplot(item_stats, aes(y = label, x = mean, color = Domain)) +
  geom_point(size = 3) +
  geom_errorbar(aes(xmin = mean - sd, xmax = mean + sd), width = 0, linewidth = .02) +
  geom_errorbar(
    aes(
      xmin = mean - 1.96 * se,
      xmax = mean + 1.96 * se
    ),
    width = 0.2,
    linewidth = 2
  ) +
#  coord_flip() +
  scale_color_manual(values = domain_colors, name = "Domain") +
  labs(
    title    = "Teacher Confidence Ratings on 32 SEB Skills",
    subtitle = "Mean ± 95% Confidence Interval by item, colored by domain",
    x        = "Skill facets",
    y        = "Score"
  ) +
  # coord_cartesian(xlim = c(3,4.25)) +
  #xlim(3, 4.25) +
  theme_minimal(base_size = 12) +
  theme(
    panel.grid.minor = element_blank(),
    legend.position  = "bottom"
  )
```

```{r Plot the ranking - Standard deviation, message=FALSE, warning=FALSE, error=FALSE, include = FALSE}
ggplot(item_stats, aes(x = label, y = mean, color = Domain)) +
  geom_point(size = 3) +
  geom_errorbar(aes(ymin = mean - sd, ymax = mean + sd), width = 0.2) +
  coord_flip() +
  scale_color_manual(values = domain_colors, name = "Domain") +
  labs(
    title    = "Teacher Confidence Ratings on 32 SEB Skills",
    subtitle = "Mean ± SD by item, colored by domain",
    x        = "Skill facets",
    y        = "Score"
  ) +
  ylim(2, 5) +
  theme_minimal(base_size = 12) +
  theme(
    panel.grid.minor = element_blank(),
    legend.position  = "bottom"
  )

```

```{r Plot the spider, message=FALSE, warning=FALSE, error=FALSE, include = TRUE}
# Define your custom grade colors here:
grade_colors <- c(
  "Grade 1" = "#1b9e77",
  "Grade 2" = "#d95f02",
  "Grade 3" = "#7570b3",
  "Grade 4" = "#e7298a"
  # Add more if needed
)

# Ensure bessi_label_vec is available
bessi_label_vec <- c(
  "Gestione dei compiti", "Gestione del tempo", "Attenzione ai dettagli", 
  "Organizzazione degli spazi e dei materiali", "Gestione degli impegni", 
  "Costanza", "Definizione degli obiettivi", "Aderenza alle regole", 
  "Prendere decisioni", "Leadership", "Persuasione", "Fare conversazione", 
  "Comunicazione", "Regolazione delle energie", "Collaborazione", 
  "Sapersi fidare e saper perdonare", "Immedesimazione", "Accoglienza emotiva", 
  "Affabilità e cordialità", "Gestione dello stress", "Ottimismo", 
  "Gestione della rabbia", "Autostima", "Resistere alle tentazioni", 
  "Pensiero astratto", "Creatività", "Espressione artistica", 
  "Interculturalità", "Elaborazione delle informazioni", "Adattabilità", 
  "Autonomia", "Introspezione"
)

# STEP 1: Compute means by grade and item
item_means_by_grade <- dcII %>%
  pivot_longer(cols = starts_with("BESSI_"), names_to = "item", values_to = "score") %>%
  group_by(School_Grade, item) %>%
  summarise(mean = mean(score, na.rm = TRUE), .groups = "drop") %>%
  pivot_wider(names_from = item, values_from = mean)

# STEP 2: Prep radar format
radar_df <- as.data.frame(item_means_by_grade)
rownames(radar_df) <- paste("Grade", radar_df$School_Grade)
radar_df$School_Grade <- NULL

# Reorder columns by BESSI_1 to BESSI_32
radar_df <- radar_df[, paste0("BESSI_", 1:32)]

# Use custom labels for each item
colnames(radar_df) <- bessi_label_vec

# Add max and min rows
max_vals <- rep(5, 32)
min_vals <- rep(2, 32)
radar_ready <- rbind(max_vals, min_vals, radar_df)

# STEP 3: Plot
# Set up plotting space (1 plot with room for legend)
# Save current graphic settings
old_par <- par(no.readonly = TRUE)

# Adjust margins to make space for title and legend
par(mar = c(1, 1, 3, 1))  # top margin increased for title

# Define your custom grade labels
grade_labels <- c(
  "Grade 1" = "Kindergarten",
  "Grade 2" = "Primary School",
  "Grade 3" = "Middle School",
  "Grade 4" = "High School"
)

# Draw radar chart
# Draw radar chart
radarchart(radar_ready,
           pcol = grade_colors[rownames(radar_df)],
           plwd = 2,
           plty = 1,
           cglcol = "grey80",
           cglty = 1,
           axislabcol = "black",
           vlcex = 0.6,
           title = "SEB Skills by Grade")

# Add legend with custom labels
legend("bottomright",
       legend = grade_labels[rownames(radar_df)],  # custom names here
       col = grade_colors[rownames(radar_df)],
       lty = 1,
       lwd = 2,
       bty = "n",
       cex = 0.8)

# Restore original plotting parameters
par(old_par)
```

```{r Table by grade, message=FALSE, warning=FALSE, error=FALSE, include = TRUE}
seb_bygrade <- dcII %>%
  pivot_longer(cols = starts_with("BESSI_"), names_to = "item", values_to = "score") %>%
  mutate(
    idx = as.integer(str_remove(item, "^BESSI_")),
    skill_label = bessi_label_vec[idx]
  ) %>%
  group_by(idx, skill_label, School_Grade) %>%
  summarise(
    mean = round(mean(score, na.rm = TRUE), 2),
    sd   = round(sd(score, na.rm = TRUE), 2),
    .groups = "drop"
  ) %>%
  mutate(mean_sd = paste0(mean, " (", sd, ")")) %>%
  select(idx, skill_label, School_Grade, mean_sd) %>%
  pivot_wider(names_from = School_Grade, values_from = mean_sd) %>%
  arrange(idx) %>%  # <<< preserves original item order
  select(-idx)

# Rename columns with grade labels
colnames(seb_bygrade) <- c(
  "Skill",
  "Kindergarten (1)", "Primary (2)", "Middle (3)", "High (4)"
)

knitr::kable(seb_bygrade , digits = 2, caption = "SEB skills ranking, divided by Grade")

```

# Mixed model
We will analyze teacher confidence in teaching SEB skills at the item level. A Cumulative Link Mixed Model will be used to test whether teacher self-efficacy and school culture predict confidence in teaching SEB skills after controlling for demographic characteristics of teachers (e.g., years of experience, school grade, average number of hours per class). Participants and items (single skills) will be included as random effects. 

We will evaluate whether including skill domains as predictors improves model fit. This approach allows us to explore whether teacher confidence varies systematically across domains.
```{r Dataset long format, message=FALSE, warning=FALSE, error=FALSE, include = FALSE}
# Reshape BESSI items into long format
dcII_long <- dcII %>%
  pivot_longer(
    cols = starts_with("BESSI_"),
    names_to = "Item",
    values_to = "Score"
  )

dcII_long$Score <- as.factor(dcII_long$Score)
# Add domain based on BESSI item number
dcII_long <- dcII_long %>%
  mutate(
    Domain = case_when(
      Item %in% paste0("BESSI_", 1:9)   ~ "SMD",   # Self-management
      Item %in% paste0("BESSI_", 10:14) ~ "SED",   # Social Engagement
      Item %in% paste0("BESSI_", 15:19) ~ "COD",   # Cooperation
      Item %in% paste0("BESSI_", 20:24) ~ "ERD",   # Emotional Resilience
      Item %in% paste0("BESSI_", 25:29) ~ "IND",   # Innovation
      Item %in% paste0("BESSI_", 30:32) ~ "COMP"   # Compound
    )
  )

# Delete rows with no scores
dcII_long  <- dcII_long [!is.na(dcII_long $Score), ]
```

```{r Cumulative Link Mixed Model, message=FALSE, warning=FALSE, error=FALSE, include = TRUE, cache=TRUE}
# I CHANGED THE LINK TO PROBIT (LATENT SCORE) E AGGIUNTO LA CACHE
# Model comparison
mod0 <- clmm(Score ~ (1 | Code) + (1 | Item), data = dcII_long, link = "probit")
mod1 <- clmm(Score ~ Role + Grade_Primary + Grade_Middle + Grade_High + Experience + Class_Time + (1 | Code) + (1 | Item), data = dcII_long, link = "probit")
mod2 <- clmm(Score ~ Role + Grade_Primary + Grade_Middle + Grade_High + Experience + Class_Time + Efficacy_Total + Culture + (1 | Code) + (1 | Item), data = dcII_long, link = "probit")
mod3 <- clmm(Score ~ Role + Grade_Primary + Grade_Middle + Grade_High + Experience + Class_Time + Efficacy_Total + Culture + Domain + (1 | Code) + (1 | Item), data = dcII_long, link = "probit")

anova(mod0, mod1, mod2, mod3)
AIC(mod0, mod1, mod2, mod3)
BIC(mod0, mod1, mod2, mod3)

# Examine parameters
summary(mod1)
summary(mod2) # best model
```
```{r Prove senza clm per velocizzare, include=FALSE}
library(lme4)
# I CHANGED THE LINK TO PROBIT (LATENT SCORE) E AGGIUNTO LA CACHE
# Model comparison
mod0 <- lmer(as.numeric(Score) ~ (1 | Code) + (1 | Item), data = dcII_long)
mod1 <- lmer(as.numeric(Score) ~ Role + Grade_Primary + Grade_Middle + Grade_High + Experience + Class_Time + (1 | Code) + (1 | Item), data = dcII_long)
mod2 <- lmer(as.numeric(Score) ~ Role + Grade_Primary + Grade_Middle + Grade_High + Experience + Class_Time + Culture + (1 | Code) + (1 | Item), data = dcII_long)
mod3 <- lmer(as.numeric(Score) ~ Role + Grade_Primary + Grade_Middle + Grade_High + Experience + Class_Time + Culture + Domain + (1 | Code) + (1 | Item), data = dcII_long)

anova(mod0, mod1, mod2, mod3)
AIC(mod0, mod1, mod2, mod3)
BIC(mod0, mod1, mod2, mod3)

# Examine parameters
summary(mod1)
summary(mod2) # best model


modx <- lmer(as.numeric(Score) ~ Role + Grade_Primary + Grade_Middle + Grade_High + Experience + Class_Time + Domain + (1 | Code) + (1 | Item), data = dcII_long)
summary(modx)
em <- emmeans::emmeans(modx, ~ Domain)
emmeans::contrast(em, method = "pairwise")

```



```{r Cumulative Link Mixed Model - Checks, message=FALSE, warning=FALSE, error=FALSE, include = FALSE}
# Some additional model checks

performance::multicollinearity(mod2) 

```

# Exploratory correlations
We explore the correlation between self-confidence in SEB skills teaching (by averaging all BESSI items) and committment in improving the ability to teach SEB skills. 
```{r Correlations, message=FALSE, warning=FALSE, error=FALSE, include = TRUE}
dcII <- dcII %>%
  mutate(BESSI_Total = rowMeans(select(., BESSI_1:BESSI_32), na.rm = TRUE))

cor.test(dcII$BESSI_Total, dcII$Commitment)
```